Approximation as Differentiation: Notes

### 2025-07-03 notes/predicate-system.tex
Start on predicate systems.
Defining predicate system.

>>>>

A \emph{predicate system} over a category $\cat{C}$ with products is the following data:
\begin{itemize}
\item for every object $X$ of $\cat{C}$, a partial order $(\Pred(X), \sqsubseteq)$ of predicates on $X$
\item for every morphism $f: X \to Y$ of $\cat{C}$:
   \begin{enumerate}
   \item a function $\reindex{-}{f}: \Pred(Y) \to \Pred(X)$ computing the reindexing or pullback of a predicate along $f$
   \item a function $\directImage{-}{f}: \Pred(X) \to \Pred(Y)$ computing the pushforward or existential
   image of a predicate along $f$
   \end{enumerate}
\end{itemize}

The pullback $\reindex{-}{-}$ is functorial.

% Reindexing [f] (pullback) and [f⟩ (pushforward or existential image) that satisfy an adjunction.
%
% Logical connectives (&&, ++, ==>, TT) and quantification (⋀).
%
% These operations satisfy standard laws such as monotonicity, closure under reindexing, etc.
